
# ch.seco.css

The ch.seco.css package provides versioned time series data
and their meta information for scientific research.
In addition, the package contains the
extract-transform-load (ETL) functionality that
sources the data from its original provider.

## Browse Time Series Data

You can use GitHub's ability to render to csv to explore the datasets

## Basic Data Consumption via opentimeseries


```r
remotes::install_github("opentsi/opentimeseries")
library(opentimeseries)

# first param `series` defaults to NULL
# fetches all series from `remote_archive`
ts <- read_open_ts(
  remote_archive = "opentsi/ch.seco.css"
)

ts
```
Given a unique time series identifier and a GitHub repo,
*opentimeseries* will return a time series and long format `data.table`.

## Basic Usage

```{r, eval=FALSE}
ts <- read_open_ts(
  remote_archive = "opentsi/ch.seco.css"
)
```
By specifying a date in addition, you can able to obtain other versions
but the most recent one. The *opentimeseries* package will simply select
the most recent release that was available at the selected date.

```{r, eval=FALSE}
ts202307 <- read_open_ts(
  remote_archive = "opentsi/ch.seco.css",
  date = "2023-07-01"
)
```
Because time series data can get revised, storing vintages is important
to monitor data revisions and benchmark forecasts. Here's a quick visual
comparison:

# please insert your main series you want to showcase visually
# to replace this example! 
```{r}
ts <- read_open_ts(series = "leading",
  remote_archive = "opentsi/ch.kof.globalbaro"
)
ts202307 <- read_open_ts(series = "leading",
  remote_archive = "opentsi/ch.kof.globalbaro"
  date = "2023-07-01"
)
a202307$id <- "leading.202307"
a$id <- sprintf("leading.202606")
ts_plot(rbind(a202307, a))
```

